Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-12 ForegroundSimulations/ms.tex
Add simulations in .npz format under data folder
From e87f065 (master):
=====================

(*) Add simulations in .npz format from achromatic Rich and Dave beams
to git repo

In ms.tex,

(*) Add a paragraph under section "foreground model"

>>>>

Our all-sky foreground model is the same as the one in \citet{thy15a}. It consists of diffuse emission \citep{deo08} and point sources. The latter is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
